Hierarchical Bayesian regression modelling predicts biochemical rection energies and facilitates quantitative modelling of cell metabolism

### 2023-10-27 paper/main.qmd
Small paper fixes.

@fig-laplace summarises the results of comparing the Laplace approximation of our
case study’s posterior distribution with the true posterior. As can be seen
from the top left plot, the Laplace method does not provide a good approximation
to the true posterior distribution, as the marginal distribution of the
total log probability density is clearly different. This was confirmed using
the Kolmogorov-Smirnov test, which is a test to differentiate two empirical
univariate distributions. The two distributions were significantly different
with a p-value indistinguishable from 0.

@@

The missing measurements did affect Maud’s ability to infer parameter values
correctly. As we can see in the [#lower left plot of @fig-missing], the model
with full metabolomics learned the true value for the displayed dissociation
constant, despite this value being far from the mean of the corresponding
marginal prior distribution, whereas the model with the missing measurements
stayed in the neighbourhood of the prior.

>>>>

@fig-laplace summarises the results of comparing the Laplace approximation of our
case study’s posterior distribution with the true posterior. As can be seen
from the top left plot, the Laplace method does not provide a good approximation
to the true posterior distribution, as the marginal distribution of the
total log probability density is clearly different. This was confirmed using
the Kolmogorov-Smirnov test, which is a test to differentiate two empirical
univariate distributions. The two distributions were significantly different
with a p-value indistinguishable from zero.

@@

The missing measurements did affect Maud’s ability to infer parameter values
correctly. The lower left plot of @fig-missing shows that the model with full
metabolomics learned the true value for the displayed dissociation constant,
despite this value being far from the mean of the corresponding marginal prior
distribution. In contrast, the model with missing measurements stayed in the
neighbourhood of the prior.

### 2023-10-27 paper/main.tex
Small paper fixes.

\title[]{Hierarchical Bayesian regression modelling predicts biochemical
rection energies and facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Below, we review the existing options in this
area, explain how Maud improves on the state of the art, describe the
intended modelling workflow and illustrate its use with an example
application.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Figure~\ref{fig-laplace} summarises the results of comparing the Laplace
approximation of our case study's posterior distribution with the true
posterior. As can be seen from the top left plot, the Laplace method
does not provide a good approximation to the true posterior
distribution, as the marginal distribution of the total log probability
density is clearly different. This was confirmed using the
Kolmogorov-Smirnov test, which is a test to differentiate two empirical
univariate distributions. The two distributions were significantly
different with a p-value indistinguishable from 0.

@@

The missing measurements did affect Maud's ability to infer parameter
values correctly. As we can see in the \#lower left plot
of~\ref{fig-missing}, the model with full metabolomics learned the true
value for the displayed dissociation constant, despite this value being
far from the mean of the corresponding marginal prior distribution,
whereas the model with the missing measurements stayed in the
neighbourhood of the prior.

>>>>

\title[]{Hierarchical Bayesian regression modelling predicts biochemical
rection energies and facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Below, we review the existing options in this
area, explain how Maud improves on the state of the art, describe the
intended modelling workflow and illustrate its use with an example
application.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, boxrule=0pt, breakable, interior hidden, enhanced]}{\end{tcolorbox}}\fi

@@

Figure~\ref{fig-laplace} summarises the results of comparing the Laplace
approximation of our case study's posterior distribution with the true
posterior. As can be seen from the top left plot, the Laplace method
does not provide a good approximation to the true posterior
distribution, as the marginal distribution of the total log probability
density is clearly different. This was confirmed using the
Kolmogorov-Smirnov test, which is a test to differentiate two empirical
univariate distributions. The two distributions were significantly
different with a p-value indistinguishable from zero.

@@

The missing measurements did affect Maud's ability to infer parameter
values correctly. The lower left plot of Figure~\ref{fig-missing} shows
that the model with full metabolomics learned the true value for the
displayed dissociation constant, despite this value being far from the
mean of the corresponding marginal prior distribution. In contrast, the
model with missing measurements stayed in the neighbourhood of the
prior.
